---
title: "Quad and Hami ROB Sensitivity Analysis"
author: "Mick Girdwood"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, error = FALSE)

black <- "#000000"
orange <- "#E69F00"
lightblue <- "#56B4E9"
green <- "#009E73"
yellow <- "#F0E442"
blue <- "#0072B2"
red <- "#D55E00"
pink <- "#CC79A7"

library(tidyverse)

within_data <- read_csv("data/processed/within_data.csv") %>%
  filter(!study %in% c("Geoghegan 2007", "Karanikas 2004", "Karanikas 2005", "Nicholas 2001",
                       "Urabe 2002", "Tate 2017", "Dalton 2011", "Hall 2015", "Noehren 2014", "Rahova 2020",
                       "Thomas 2013", "Balki 2019", "Rhatomy", "Sullivan 2022"))

# filtering studies that were included in hip review (where no limit on publication year), but need to remove forthis review
casecontrol <- read_csv("data/processed/casecontrol.csv") %>%
  filter(!study %in% c("Geoghegan 2007", "Karanikas 2004", "Karanikas 2005", "Nicholas 2001",
                       "Urabe 2002", "Tate 2017", "Dalton 2011", "Hall 2015", "Noehren 2014", "Rahova 2020",
                       "Thomas 2013", "Balki 2019", "Rhatomy", "Sullivan 2022"))

rob <- read_csv("data/processed/rob_final.csv") %>%
  mutate(rob_analysis = case_when(
    outcome_c != "Low" & blinding_assessor_c != "Low" & selection_c != "Low" ~ "High",
    TRUE ~ "Low"))

within_data <- left_join(within_data, rob %>% select(study, rob_analysis), by = "study")
casecontrol <- left_join(casecontrol, rob %>% select(study, rob_analysis), by = "study")


## Functions:


pointsfunction <- function(data){
  data %>%
    select(ci.ub, x) %>% 
    bind_rows(., data %>% 
                select(ci.lb, x) %>% 
                rename(ci.ub = ci.lb) %>% 
                arrange(desc(x)))
}

pi_pointsfunction <- function(data){
  data %>%
    select(pi.ub, x) %>% 
    bind_rows(., data %>% 
                select(pi.lb, x) %>% 
                rename(pi.ub = pi.lb) %>% 
                arrange(desc(x)))
}

mv_plotfunction_rob <- function(model, model2){
  
  knot_pos <- NULL # set to 0 for logic to work later
  
  moderator <- as.character(model$call$mods[2]) # get the moderator variable
  data <- model$data # get the data
  
  last_timepoint <- round(max(data$timepoint_mean),0)
  
  total_k  <- model$k
  total_studies <- data %>% filter(!is.na(vi)) %>% summarise(n = length(unique(study))) %>% as.numeric()
  total_n <- data %>% group_by(study) %>% arrange(timepoint) %>% slice(1) %>% ungroup()  %>% filter(!is.na(vi)) %>% summarise(n = sum(acl_n)) %>% as.numeric
  
  
  if (str_detect(moderator, "rcs")) { # if a rcs is used, extract the information
    spline <- as.list(model$formula.mods[[2]][[3]]) 
    knot_pos <- unlist(spline[sapply(spline, is.numeric)]) # this gets the vector of knot positions or no. of knots
  }
  
  # depending on the type od moderator (i.e. log, linear, rcs...) calculate the predicted curve points
  mod_type <- if (str_detect(moderator, "log")) {
    
    #log
    points <- data.frame(predict(robust(model, cluster = cohort, clubSandwich = TRUE), 
                                 newmods = log(seq(1,100, length = 100)),
                                 transf = exp
    )) %>% mutate(x = row_number())
    
  } else if (str_detect(moderator, "poly")) {
    
    # poly
    points <- data.frame(predict(robust(model, cluster = cohort, clubSandwich = TRUE), 
                                 newmods=unname(poly(seq(1,100, length = 100), degree = 2, raw=TRUE)),
                                 transf = exp
    )) %>% mutate(x = row_number())
    
  } else if (length(knot_pos) == 3) {
    
    # 3 knot rcs
    knots <- attr(rcs(model.matrix(model)[,2], knot_pos), "parms")
    points <- data.frame(predict(robust(model, cluster = cohort, clubSandwich = TRUE), 
                                 newmods=rcspline.eval(seq(1,100, length = 100), knots, inclx=TRUE),
                                 transf = exp)) %>% 
      mutate(x = row_number())
    
  } else if (length(knot_pos) == 1) { # i.e. cases where only the number of knots is given
    
    # 3 knot rcs
    knots <- attr(rcs(data$timepoint_mean, as.numeric(knot_pos)), "parms") # use model data to get knot positions
    points <- data.frame(predict(robust(model, cluster = cohort, clubSandwich = TRUE), 
                                 newmods=rcspline.eval(seq(1,100, length = 100), knots, inclx=TRUE),
                                 transf = exp)) %>% 
      mutate(x = row_number())
    
  } else if (length(knot_pos) == 4) {
    
    # 4 knot rcs
    knots <- attr(rcs(model.matrix(model)[,2], knot_pos), "parms")
    points <- data.frame(predict(robust(model, cluster = cohort, clubSandwich = TRUE), 
                                 newmods=rcspline.eval(seq(1,100, length = 100), knots, inclx=TRUE),
                                 transf = exp)) %>% 
      mutate(x = row_number())
    
  } else {
    # Linear
    points <- data.frame(predict(robust(model, cluster = cohort, clubSandwich = TRUE), 
                                 newmods = seq(1,100, length = 100),
                                 transf = exp)) %>% mutate(x = row_number())
  }
  
  # calculate ci points
  ci <-  pointsfunction(points)
  
  ci <- ci %>% filter(x < last_timepoint + 6)
  points <- points %>% filter(x < last_timepoint + 6)
  
  
  #### 2nd model
  
  knot_pos2 <- NULL # set to 0 for logic to work later
  
  moderator2 <- as.character(model2$call$mods[2]) # get the moderator variable
  data2 <- model2$data # get the data
  
  last_timepoint2 <- round(max(data2$timepoint_mean),0)
  
  if (str_detect(moderator, "rcs")) { # if a rcs is used, extract the information
    spline2 <- as.list(model2$formula.mods[[2]][[3]]) 
    knot_pos2 <- unlist(spline[sapply(spline, is.numeric)]) # this gets the vector of knot positions or no. of knots
  }
  
  # depending on the type od moderator (i.e. log, linear, rcs...) calculate the predicted curve points
  mod_type2 <- if (str_detect(moderator, "log")) {
    
    #log
    points2 <- data.frame(predict(robust(model2, cluster = cohort, clubSandwich = TRUE), 
                                 newmods = log(seq(1,100, length = 100)),
                                 transf = exp
    )) %>% mutate(x = row_number())
    
  } else if (str_detect(moderator, "poly")) {
    
    # poly
    points2 <- data.frame(predict(robust(model2, cluster = cohort, clubSandwich = TRUE), 
                                 newmods=unname(poly(seq(1,100, length = 100), degree = 2, raw=TRUE)),
                                 transf = exp
    )) %>% mutate(x = row_number())
    
  } else if (length(knot_pos) == 3) {
    
    # 3 knot rcs
    knots2 <- attr(rcs(model.matrix(model2)[,2], knot_pos2), "parms")
    points2 <- data.frame(predict(robust(model2, cluster = cohort, clubSandwich = TRUE), 
                                 newmods=rcspline.eval(seq(1,100, length = 100), knots2, inclx=TRUE),
                                 transf = exp)) %>% 
      mutate(x = row_number())
    
  } else if (length(knot_pos2) == 1) { # i.e. cases where only the number of knots is given
    
    # 3 knot rcs
    knots2 <- attr(rcs(data2$timepoint_mean, as.numeric(knot_pos2)), "parms") # use model data to get knot positions
    points2 <- data.frame(predict(robust(model2, cluster = cohort, clubSandwich = TRUE), 
                                 newmods=rcspline.eval(seq(1,100, length = 100), knots2, inclx=TRUE),
                                 transf = exp)) %>% 
      mutate(x = row_number())
    
  } else if (length(knot_pos2) == 4) {
    
    # 4 knot rcs
    knots2 <- attr(rcs(model.matrix(model2)[,2], knot_pos2), "parms")
    points2 <- data.frame(predict(robust(model2, cluster = cohort, clubSandwich = TRUE), 
                                 newmods=rcspline.eval(seq(1,100, length = 100), knots2, inclx=TRUE),
                                 transf = exp)) %>% 
      mutate(x = row_number())
    
  } else {
    # Linear
    points2 <- data.frame(predict(robust(model2, cluster = cohort, clubSandwich = TRUE), 
                                 newmods = seq(1,100, length = 100),
                                 transf = exp)) %>% mutate(x = row_number())
  }
  
  # calculate ci points
  ci2 <-  pointsfunction(points2)
  
  ci2 <- ci2 %>% filter(x < last_timepoint2 + 6)
  points2 <- points2 %>% filter(x < last_timepoint2 + 6)
  
  data3 <- data2 %>% filter(rob_analysis == "Low")
  
  total_k2  <- model2$k
  total_studies2 <- data3 %>% filter(!is.na(vi)) %>% summarise(n = length(unique(study))) %>% as.numeric()
  total_n2 <- data3 %>% distinct(cohort, .keep_all = TRUE)  %>% filter(!is.na(vi)) %>% summarise(n = sum(acl_n)) %>% as.numeric
  
  
  
  total_nrob <- paste0(total_n, " - ", total_n - total_n2)
  rob <- total_studies - total_studies2

    
    
    # plot data and predicted model
    plot <- data %>%
      ggplot(aes(x = timepoint_mean, y = exp(yi), group = cohort)) +
      geom_point(aes(size = acl_n, colour = rob_analysis), alpha = 0.3) + 
      scale_colour_manual(values = c("red", "black"), name = "ROB") +
      geom_line(alpha = 0.8, colour = "grey") + 
      scale_y_continuous(breaks = c(0.6, 0.8, 1.0, 1.2), labels = c("-40%", "-20%", "0%", "+20%")) +
      #scale_y_continuous(labels = scales::percent, limits = c(-0.75, 0.25)) +
      scale_x_continuous(breaks = c(0, 12, 24, 60, 120), labels = c(0, 1, 2, 5, 10)) +
      coord_cartesian(xlim = c(0,100), ylim = c(0.5, 1.2)) +
      scale_size(range = c(0, 10)) +
      labs(x = "Time since surgery (Months)", y = "Percentage Deficit", colour = "Measure", size = "Participants (n)") +
      #geom_smooth(aes(x = timepoint_mean, y = yi), method = "lm", colour = "green", inherit.aes = FALSE) +
      #geom_abline(intercept = -0.2198, slope = 0.0014, colour = "red") +
      geom_line(data = points, aes(x = x, y = pred), colour = "red", linewidth = 1.3, inherit.aes = FALSE) +
      geom_polygon(data = ci, aes(x = x, y = ci.ub), fill = "red",  alpha = 0.1, inherit.aes = FALSE) +
      geom_line(data = points2, aes(x = x, y = pred), colour = "blue", linewidth = 1.3, inherit.aes = FALSE) +
      geom_polygon(data = ci2, aes(x = x, y = ci.ub), fill = "blue",  alpha = 0.1, inherit.aes = FALSE) +
      annotate(geom = "text", x = 100, y = 0.5, label = paste0(rob, " studies removed"), family = "Karla", hjust = 1) +
      annotate(geom = "text", x = 100, y = 0.55, label = paste0("n = ", total_nrob), family = "Karla", hjust = 1) +
      theme_mgpub() +
            theme(panel.grid.major.x = element_line(linewidth = rel(0.5), linetype = 2))
  
  return(plot)
  
}
```

```{r libraries}
library(metafor) # for meta-analysis
library(clubSandwich) # for covariance matrix and robust ci estimates
library(rms) # for fitting splines
library(ellipse)
library(ggpubr)
library(mgfunctions)
library(kableExtra)
```

# 1. Quadriceps Strength - Within Person

```{r quad withindata}
# Generate the within person quad strength data
quad <- within_data %>%
  rename(acl_graft_group = graft_group) %>% 
  filter(str_detect(measure, "quad")) %>% # take all quad based outcomes
  filter(timepoint_mean >0.2, # remove pre-operative data
         timepoint_mean < 120, # remove >10 year data
         str_detect(graft, "contralateral|Contralateral", negate = TRUE)) %>%  # remove any contralateral grafts
  mutate(es_id = row_number()) %>% # effect size id number for use in random effects
  mutate(measure_2 = case_when( # classify different outcomes into subgroups:
    str_detect(measure, "mvic|hhd") ~ "Isometric",
    str_detect(measure, "isk con 180|isk con 230|isk con 240|isk con 300") ~ "Fast Isokinetic",
    str_detect(measure, "isk con 30|isk con 60|isk con 90|isk con 120") ~ "Slow Isokinetic"
  )) %>%
  filter(!is.na(measure_2)) 

# Reducing timepoint down to categories (3, 6, 12, 24, 48, 96 months post)
# not using this at the moment but keeping code here for now
quad_cat <- quad %>%
  mutate(timepoint_cut = cut(timepoint_mean, 
                             breaks = c(0, 4.5, 9, 18, 36, 72, Inf), 
                             labels = c(3, 6, 12, 24, 48, 96))) 
  #group_by(cohort, timepoint_cut, group, measure_2) %>%
  # if multiple timepoints allocated to same category, take the closest to the categorical timepoint
  #slice(which.min(abs(timepoint_mean - as.numeric(as.character(timepoint_cut))))) %>% 
  #ungroup()

# separate subgroups of data based on contraction type
# Some studies report multiple outcomes in the same subgroup
# Case by case removal of data 
# Generally:
# for fast if they have isk con 180 use that if possible, otherwise use speed closest to this.
# for slow use isk con 60, or 90

fastdata <- quad_cat %>% filter(measure_2 == "Fast Isokinetic") %>%
  filter(!(cohort == "Bailey 2019" & measure == "quad isk con 300"),
         !(cohort == "Drocco 2017" & measure == "quad isk con 240"),
         !(cohort == "Kyritsis 2016" & measure == "quad isk con 300"),
         !(cohort == "Laudner 2015" & measure == "quad isk con 300"),
         !(cohort == "Tourville 2014" & measure == "quad isk con 300"),
         !(cohort == "Welling 2020" & measure == "quad isk con 300"),
         !(cohort == "Welling 2018b" & measure == "quad isk con 300")
         ) 
slowdata <- quad_cat %>% filter(measure_2 == "Slow Isokinetic") %>%
  filter(!(cohort == "Li 2022" & measure == "quad isk con 30"),
         !(cohort == "Siney 2010" & measure == "quad isk con 90"),
         !(cohort == "Zult 2017" & measure == "quad isk con 120"),
         !(cohort == "Pamukoff 2018" & measure == "quad isk con 120"))
isodata <- quad_cat %>% filter(measure_2 == "Isometric") %>%
  filter(!(cohort == "Karanikas 2005" & measure == "quad mvic 0"),
         !(cohort == "Labanca 2018" & measure == "quad mvic 30"),
         !(cohort == "Labanca 2016" & measure == "quad mvic 30"),
         !(cohort == "Wongcharoenwatana 2019" & measure == "quad mvic 90 hhd prone"))

```

### Specify covariance matrix

```{r quadwithin covariance, include=TRUE}

fastV <- impute_covariance_matrix(vi = fastdata$vi, 
                                  cluster = fastdata$cohort, # cluster is cohort (not study)
                                  ti = fastdata$timepoint_mean, # timepoint 
                                  ar1 = 0.85, # auto-correlation between timepoints
                                  check_PD = TRUE, # check positive definite afterwards
                                  smooth_vi = TRUE,
                                  return_list = FALSE) # return the full matrix

slowV <- impute_covariance_matrix(vi = slowdata$vi, 
                                  cluster = slowdata$cohort,
                                  ti = slowdata$timepoint_mean,
                                  ar1 = 0.85,
                                  smooth_vi = TRUE,
                                  return_list = FALSE)

isoV <- impute_covariance_matrix(vi = isodata$vi, 
                                  cluster = isodata$cohort,
                                  ti = isodata$timepoint_mean,
                                  ar1 = 0.85,
                                  check_PD = TRUE,
                                  smooth_vi = TRUE,
                                 return_list = FALSE)

```

### Slow Isokinetic Quadriceps

```{r quadwithin slowfinal}
slow_mv <- rma.mv(yi, slowV, 
                  mods = ~rcs(timepoint_mean, 4), 
                  data = slowdata, 
                  random = list(~ timepoint_mean|cohort),
                  struct = c("CAR"))

slow_mv_rob <- rma.mv(yi, slowV, 
                  mods = ~rcs(timepoint_mean, 4), 
                  data = slowdata, 
                  random = list(~ timepoint_mean|cohort),
                  struct = c("CAR"),
                  subset = rob_analysis == "Low")

mv_plotfunction_rob(slow_mv, slow_mv_rob)

```


### Fast Isokinetic Quadriceps

```{r quadwithin fastfinal}
fast_mv <- rma.mv(yi, fastV, 
                  mods = ~rcs(timepoint_mean, 4), 
                  data = fastdata, 
                  random = list(~ timepoint_mean|cohort),
                  struct = c("CAR"))

fast_mv_rob <- rma.mv(yi, fastV, 
                  mods = ~rcs(timepoint_mean, 4), 
                  data = fastdata, 
                  random = list(~ timepoint_mean|cohort),
                  struct = c("CAR"),
                  subset = rob_analysis == "Low")

mv_plotfunction_rob(fast_mv, fast_mv_rob)

```


### Isometric Quadriceps

```{r quadwithin isofinal}
iso_mv <- rma.mv(yi, isoV, 
                  mods = ~rcs(timepoint_mean, 4), 
                  data = isodata, 
                  random = list(~ timepoint_mean|cohort),
                  struct = c("CAR"))

iso_mv_rob <- rma.mv(yi, isoV, 
                  mods = ~rcs(timepoint_mean, 4), 
                  data = isodata, 
                  random = list(~ timepoint_mean|cohort),
                  struct = c("CAR"),
                  subset = rob_analysis == "Low")

mv_plotfunction_rob(iso_mv, iso_mv_rob)

```


##########

# 2. Hamstring Strength - Within Person

```{r hs withindata}

# Data for Hamstring
hs <- within_data %>%
  rename(acl_graft_group = graft_group) %>%
  filter(str_detect(measure, "hs")) %>%
 filter(timepoint_mean >0.2, # remove pre-operative data
         timepoint_mean < 120, # remove >10 year data
         str_detect(graft, "contralateral|Contralateral", negate = TRUE)) %>%  # remove any contralateral grafts
  mutate(es_id = row_number()) %>%
  mutate(measure_2 = case_when(
    str_detect(measure, "mvic|hhd") ~ "Isometric",
    str_detect(measure, "isk con 180|isk con 230|isk con 240|isk con 300") ~ "Fast Isokinetic",
    str_detect(measure, "isk con 30|isk con 60|isk con 90|isk con 120") ~ "Slow Isokinetic"
  )) %>%
  filter(!is.na(measure_2))

# Reducing timepoint down to categories (3, 6, 12, 24, 48, 96 months post)
# not using this at the moment but keeping code here for now

hs_cat <- hs %>%
  mutate(timepoint_cut = cut(timepoint_mean, 
                             breaks = c(0, 4.5, 9, 18, 36, 72, Inf), 
                             labels = c(3, 6, 12, 24, 48, 96))) 
  #group_by(cohort, timepoint_cut, measure_2) %>%
  # if multiple timepoints allocated to same category, take the closest to the categorical timepoint
  #slice(which.min(abs(timepoint_mean - as.numeric(as.character(timepoint_cut))))) %>% 
  #ungroup()

# separate subgroups of data based on contraction type
# Some studies report multiple outcomes in the same subgroup
# Case by case removal of data 
# Generally:
# for fast if they have isk con 180 use that if possible, otherwise use speed closest to this.
# for slow use isk con 60, or 90

hs_fastdata <- hs_cat %>% filter(measure_2 == "Fast Isokinetic") %>%
  filter(!(cohort == "Drocco 2017" & measure == "hs isk con 240"),
         !(cohort == "Kyritsis 2016" & measure == "hs isk con 300"),
         !(cohort == "Laudner 2015" & measure == "hs isk con 300"),
         !(cohort == "Tourville 2014" & measure == "hs isk con 300"),
         !(cohort == "Welling 2020" & measure == "hs isk con 300"),
         !(cohort == "Welling 2018b" & measure == "hs isk con 300"))
hs_slowdata <- hs_cat %>% filter(measure_2 == "Slow Isokinetic") %>%
  filter(!(cohort == "Lee 2019" & measure == "hs isk con 60 - deep"),
         !(cohort == "Kim 2011" & measure == "hs isk con 90 hyperflex"),
         !(cohort == "Siney 2010" & measure == "hs isk con 90"),
         !(cohort == "McRae 2013" & measure == "hs isk con 60 supine"),
         !(cohort == "Li 2022" & measure == "hs isk con 30"),
         !(cohort == "Jiang 2012" & measure == "hs isk con 120"),
         !(cohort == "Zult 2017" & measure == "hs isk con 120")
         )
hs_isodata <- hs_cat %>% filter(measure_2 == "Isometric") %>%
  filter(!(cohort == "Hu 2020" & measure == "hs mvic 30 hhd"),
         !(cohort == "Hu 2020" & measure == "hs mvic 60 hhd"),
         !(cohort == "Ardern 2010" & measure == "hs mvic 30"),
         !(cohort == "Ardern 2010" & measure == "hs mvic 105"))
```

### Specify covariance matrix
```{r hswithin covariance, include=TRUE}

hs_fastV <- impute_covariance_matrix(vi = hs_fastdata$vi, 
                                  cluster = hs_fastdata$cohort,
                                  ti = hs_fastdata$timepoint_mean,
                                  ar1 = 0.85,
                                  check_PD = TRUE,
                                  smooth_vi = TRUE, 
                                  return_list = FALSE)

hs_slowV <- impute_covariance_matrix(vi = hs_slowdata$vi, 
                                  cluster = hs_slowdata$cohort,
                                  ti = hs_slowdata$timepoint_mean,
                                  ar1 = 0.85,
                                  smooth_vi = TRUE,
                                  return_list = FALSE)

hs_isoV <- impute_covariance_matrix(vi = hs_isodata$vi, 
                                 cluster = hs_isodata$cohort,
                                 ti = hs_isodata$timepoint_mean,
                                 ar1 = 0.85,
                                 check_PD = TRUE,
                                 smooth_vi = TRUE,
                                 return_list = FALSE)

```

### Slow Isokinetic Hamstrings

```{r hswithin slowfinal}
hs_slow_mv <- rma.mv(yi, hs_slowV, 
                    mods = ~rcs(timepoint_mean, 4),
                    data = hs_slowdata, 
                    random = list(~ timepoint_mean|cohort),
                    struct = c("CAR"))

hs_slow_mv_rob <- rma.mv(yi, hs_slowV, 
                    mods = ~rcs(timepoint_mean, 4),
                    data = hs_slowdata, 
                    random = list(~ timepoint_mean|cohort),
                    struct = c("CAR"),
                    subset = rob_analysis == "Low")

mv_plotfunction_rob(hs_slow_mv, hs_slow_mv_rob)


```


### Fast Isokinetic Hamstrings

```{r hswithin fastfinal}
hs_fast_mv <- rma.mv(yi, hs_fastV, 
                     mods = ~rcs(timepoint_mean, 4),
                     data = hs_fastdata, 
                     random = list(~ timepoint_mean|cohort),
                     struct = c("CAR"))

hs_fast_mv_rob <- rma.mv(yi, hs_fastV, 
                     mods = ~rcs(timepoint_mean, 4),
                     data = hs_fastdata, 
                     random = list(~ timepoint_mean|cohort),
                     struct = c("CAR"),
                     subset = rob_analysis == "Low")

mv_plotfunction_rob(hs_fast_mv, hs_fast_mv_rob)

```


### Isometric Hamstrings

```{r hswithin isofinal}
hs_iso_mv <- rma.mv(yi, hs_isoV, 
                     mods = ~log(timepoint_mean),
                     data = hs_isodata, 
                     random = list(~ timepoint_mean|cohort),
                     struct = c("CAR"))

hs_iso_mv_rob <- rma.mv(yi, hs_isoV, 
                     mods = ~log(timepoint_mean),
                     data = hs_isodata, 
                     random = list(~ timepoint_mean|cohort),
                     struct = c("CAR"),
                     subset = rob_analysis == "Low")

mv_plotfunction_rob(hs_iso_mv, hs_iso_mv_rob)

```

####################


# 3. Quadriceps Strength - Case Control

```{r quad ccdata}
# Generate the within person quad strength data

quadcont <- casecontrol %>%
  filter(str_detect(measure, "quad")) %>%
  mutate(es_id = row_number(),
         timepoint_mean = acl_timepoint_mean,
         group = 1) %>%
   filter(timepoint_mean >0.2, # no pre-operative data
         timepoint_mean < 120) %>%
  mutate(measure_2 = case_when(
    str_detect(measure, "mvic|hhd") ~ "Isometric",
    str_detect(measure, "isk con 180|isk con 230|isk con 240|isk con 300") ~ "Fast Isokinetic",
    str_detect(measure, "isk con 30|isk con 60|isk con 90|isk con 120") ~ "Slow Isokinetic"
  )) %>%
  filter(!is.na(measure_2)) %>%
  #filter(timepoint_mean < 100) %>%
  filter(!(cohort == "Laudner 2015" & measure == "quad isk con 300"), # remove where multiple effect sizes in same measure group
         !(cohort == "Pamukoff 2018" & measure == "quad isk con 120"),
         !(cohort == "Tourville 2014" & measure == "quad isk con 300"),
         !(cohort == "Zult 2017" & measure == "quad isk con 120"))

# Reducing timepoint down to categories (3, 6, 12, 24, 48, 96 months post)
# not using this at the moment but keeping code here for now
quadcont_cat <- quadcont %>%
  mutate(timepoint_cut = cut(timepoint_mean, 
                             breaks = c(0, 4.5, 9, 18, 36, 72, Inf), 
                             labels = c(3, 6, 12, 24, 48, 96)))
  #group_by(cohort, timepoint_cut, group, measure_2) %>%
  # if multiple timepoints allocated to same category, take the closest to the categorical timepoint
  #slice(which.min(abs(timepoint_mean - as.numeric(as.character(timepoint_cut))))) %>% 
  #ungroup()

# separate subgroups of data based on contraction type

fastcont <- quadcont_cat %>% filter(measure_2 == "Fast Isokinetic")
slowcont <- quadcont_cat %>% filter(measure_2 == "Slow Isokinetic")
isocont <- quadcont_cat %>% filter(measure_2 == "Isometric")
```

### Specify covariance matrix

```{r quadcc covariance, include=TRUE}

qcont_slowV <- impute_covariance_matrix(vi = slowcont$vi, 
                                  cluster = slowcont$cohort,
                                  ti = slowcont$timepoint_mean,
                                  ar1 = 0.85,
                                  check_PD = TRUE,
                                  return_list = FALSE)

qcont_fastV <- impute_covariance_matrix(vi = fastcont$vi, 
                                  cluster = fastcont$cohort,
                                  ti = fastcont$timepoint_mean,
                                  ar1 = 0.85,
                                  check_PD = TRUE,
                                  return_list = FALSE)

qcont_isoV <- impute_covariance_matrix(vi = isocont$vi, 
                                 cluster = isocont$cohort,
                                 ti = isocont$timepoint_mean,
                                 ar1 = 0.85,
                                 check_PD = TRUE,
                                 return_list = FALSE)


```

## Final models

### Slow Isokinetic Quadriceps

```{r quadcc slowfinal}
qcont_slow_mv <- rma.mv(yi, qcont_slowV, 
                        mods = ~log(timepoint_mean),
                        data = slowcont, 
                        random = list(~ timepoint_mean|cohort),
                        struct = c("CAR"))

qcont_slow_mv_rob <- rma.mv(yi, qcont_slowV, 
                        mods = ~log(timepoint_mean),
                        data = slowcont, 
                        random = list(~ timepoint_mean|cohort),
                        struct = c("CAR"),
                        subset = rob_analysis == "Low")

mv_plotfunction_rob(qcont_slow_mv, qcont_slow_mv_rob)

```


### Fast Isokinetic Quadriceps

```{r quadcc fastfinal}
qcont_fast_mv <- rma.mv(yi, qcont_fastV, 
                              mods = ~log(timepoint_mean),
                              data = fastcont, 
                              random = list(~ timepoint_mean|cohort),
                              struct = c("CAR"))

qcont_fast_mv_rob <- rma.mv(yi, qcont_fastV, 
                              mods = ~log(timepoint_mean),
                              data = fastcont, 
                              random = list(~ timepoint_mean|cohort),
                              struct = c("CAR"),
                              subset = rob_analysis == "Low")

mv_plotfunction_rob(qcont_fast_mv, qcont_fast_mv_rob) + scale_colour_manual(values = c("black"), name = "ROB")

```


### Isometric Quadriceps

```{r quadcc isofinal}
qcont_iso_mv <- rma.mv(yi, qcont_isoV, 
                        mods = ~log(timepoint_mean),
                        data = isocont, 
                        random = list(~ timepoint_mean|cohort),
                        struct = c("CAR"))

qcont_iso_mv_rob <- rma.mv(yi, qcont_isoV, 
                        mods = ~log(timepoint_mean),
                        data = isocont, 
                        random = list(~ timepoint_mean|cohort),
                        struct = c("CAR"),
                        subset = rob_analysis == "Low")

mv_plotfunction_rob(qcont_iso_mv, qcont_iso_mv_rob)

```


##

# 4. Hamstring Strength - Case Control

```{r hs ccdata}

hscont <- casecontrol %>%
  filter(str_detect(measure, "hs")) %>%
  mutate(es_id = row_number(),
         timepoint_mean = acl_timepoint_mean,
         group = 1) %>%
   filter(timepoint_mean >0.2, # no pre-operative data
         timepoint_mean < 120) %>%
  mutate(measure_2 = case_when(
    str_detect(measure, "mvic|hhd") ~ "Isometric",
    str_detect(measure, "isk con 180|isk con 230|isk con 240|isk con 300") ~ "Fast Isokinetic",
    str_detect(measure, "isk con 30|isk con 60|isk con 90|isk con 120") ~ "Slow Isokinetic"
  )) %>%
  filter(!is.na(measure_2)) %>%
  filter(timepoint_mean < 100) %>%
  filter(!(cohort == "Laudner 2015" & measure == "hs isk con 300"), # remove where multiple effect sizes in same measure group
         !(cohort == "Tourville 2014" & measure == "hs isk con 300"),
         !(cohort == "Zult 2017" & measure == "hs isk con 120"))

# Reducing timepoint down to categories (3, 6, 12, 24, 48, 96 months post)
# not using this at the moment but keeping code here for now

hscont_cat <- hscont %>%
  mutate(timepoint_cut = cut(timepoint_mean, 
                             breaks = c(0, 4.5, 9, 18, 36, 72, Inf), 
                             labels = c(3, 6, 12, 24, 48, 96))) 
  #group_by(cohort, timepoint_cut, measure_2) %>%
  # if multiple timepoints allocated to same category, take the closest to the categorical timepoint
  #slice(which.min(abs(timepoint_mean - as.numeric(as.character(timepoint_cut))))) %>% 
  #ungroup()

# separate subgroups of data based on contraction type

hs_fastcont <- hscont_cat %>% filter(measure_2 == "Fast Isokinetic")
hs_slowcont <- hscont_cat %>% filter(measure_2 == "Slow Isokinetic")
hs_isocont <- hscont_cat %>% filter(measure_2 == "Isometric")
```

### Specify covariance matrix


```{r hscc covariance, include=TRUE}

hcont_fastV <- impute_covariance_matrix(vi = hs_fastcont$vi, 
                                        cluster = hs_fastcont$cohort,
                                        ti = hs_fastcont$timepoint_mean,
                                        ar1 = 0.85,
                                        check_PD = TRUE,
                                        smooth_vi = TRUE, 
                                        return_list = FALSE)

hcont_slowV <- impute_covariance_matrix(vi = hs_slowcont$vi, 
                                        cluster = hs_slowcont$cohort,
                                        ti = hs_slowcont$timepoint_mean,
                                        ar1 = 0.85,
                                        smooth_vi = TRUE,
                                        return_list = FALSE)

hcont_isoV <- impute_covariance_matrix(vi = hs_isocont$vi, 
                                       cluster = hs_isocont$cohort,
                                       ti = hs_isocont$timepoint_mean,
                                       ar1 = 0.85,
                                       check_PD = TRUE,
                                       smooth_vi = TRUE,
                                       return_list = FALSE)

```

## Final models

### Slow Isokinetic Hamstrings

```{r hscc slowfinal}
hcont_slow_mv <- rma.mv(yi, hcont_slowV, 
                        mods = ~log(timepoint_mean),
                        data = hs_slowcont, 
                        random = list(~ timepoint_mean|cohort),
                        struct = c("CAR"))

hcont_slow_mv_rob <- rma.mv(yi, hcont_slowV, 
                        mods = ~log(timepoint_mean),
                        data = hs_slowcont, 
                        random = list(~ timepoint_mean|cohort),
                        struct = c("CAR"),
                        subset = rob_analysis == "Low")

mv_plotfunction_rob(hcont_slow_mv, hcont_slow_mv_rob)

```


### Fast Isokinetic Hamstrings

```{r hscc fastfinal}
hcont_fast_mv <- rma.mv(yi, hcont_fastV, 
                        mods = ~log(timepoint_mean),
                        data = hs_fastcont, 
                        random = list(~ timepoint_mean|cohort),
                        struct = c("CAR"))

hcont_fast_mv_rob <- rma.mv(yi, hcont_fastV, 
                        mods = ~log(timepoint_mean),
                        data = hs_fastcont, 
                        random = list(~ timepoint_mean|cohort),
                        struct = c("CAR"),
                        subset = rob_analysis == "Low")

mv_plotfunction_rob(hcont_fast_mv, hcont_fast_mv_rob) + scale_colour_manual(values = c("black"), name = "ROB")
```


### Isometric Hamstrings

```{r hscc isofinal}
hcont_iso_mv <- rma.mv(yi, hcont_isoV, 
                       mods = ~poly(timepoint_mean, degree = 2, raw = TRUE),
                       data = hs_isocont, 
                       random = list(~ timepoint_mean|cohort),
                       struct = c("CAR"))

hcont_iso_mv_rob <- rma.mv(yi, hcont_isoV, 
                       mods = ~poly(timepoint_mean, degree = 2, raw = TRUE),
                       data = hs_isocont, 
                       random = list(~ timepoint_mean|cohort),
                       struct = c("CAR"),
                       subset = rob_analysis == "Low")

mv_plotfunction_rob(hcont_iso_mv, hcont_iso_mv_rob)
```

